---
title: "Listening to Mothers IV: First Full Survey Report Draft Outline with Item Contents and Subgroup Analyses Clarity"
author: "Ruby Barnard-Mayers"
date: "2025-08-13"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---
```{r, include = FALSE}
source("~/Documents/2025-2026/LTM/Listening-to-Mothers/Data Cleaning.R")
library(survey)
library(ggplot2)
library(ggsurvey)

des <- svydesign(ids = ~1, weights = ~wght, data = LTM_final)
```

## New Mothers Share Views and Experiences of Childbearing: Results from the Fourth National Listening to Mothers Survey

### Chapter 1. Before and During Pregnancy

Before pregnancy

-   Past births/NUMB_BIRTH and parity of respondents
```{r echo = FALSE}
ggbarweight(LTM_final, NUMB_BIRTH, wght) + theme_classic()
```

-   Index pregnancy intention/PREG_INT

-   Health issues during 3 months before index pregnancy

-   Physical conditions/PREPREG_PHYSCOND

-   Mental health conditions/PREPREG_MHCOND

-   BMI before pregnancy/PREPREG_WEIGHT and HEIGHT

Pregnancy care team: main type of prenatal maternity care provider,
choice

-   Most frequent type of pregnancy provider/PROVIDER
    -   Proposed exhibit: primary prenatal use of physicians and
        midwives by race and ethnicity and by private vs Medicaid
        insurance
        -   Narrative could report on whether there were differences in
            type of provider by parity and by whether born in US or
            abroad
-   Whether had choice about pregnancy provider/PROVIDERCHOICE
    -   Proposed exhibit: breakdown by race and ethnicity and private vs
        Medicaid insurance
        -   Narrative could report on whether there were differences in
            choice by whether born in US or abroad, whether speaks Eng
            or something else at home, by disability status (any vs no
            types), by metro vs non-metro residence
-   Whether had doula support during pregnancy/DOULA [x-ref to
    childbirth and pp doula results]
    -   Proposed exhibit: breakdown by race and ethnicity and private vs
        Medicaid insurance
        -   Narrative could report on whether there were differences by
            parity, by mother’s country of birth, by disability status,
            by metro vs non-metro residence
    -   If yes, how doula supported/DOULA1
    -   Possible doula quotes for margins/DOULA3
    -   [appropriate to consolidate doula results across phases of care;
        propose that this occurs when reporting birth doula experiences;
        maybe x-ref here]
-   See also re preg care team: mental health help and childbirth
    education, later in this chapter

Prenatal care: Learning about pregnancy and first prenatal visit,
setting, remote care/equipment, solo/group

-   Learning about pregnancy, initiating and not having prenatal care,
    care setting
    -   Weeks pregnant when learned about pregnancy/LEARNED1; average
        and range
    -   No prenatal care/LEARNED2/98 (and comment that those with no pnc
        or late initiation of pnc less likely to participate in survey
        so our data probably underestimate those folks)
        -   Narrative could report no prenatal care by race and
            ethnicity; private vs Medicaid insurance; pregnancy
            intention/PREG_INT = 1 or 2 versus 4 (and decide where
            3/later best fits); mental health (PREPREG_MHCOND = any 1-5
            and/or BOTHER – explore screen positive for depression,
            anxiety, and/or psychological distress); by SOCIALNEED
            cumulative social needs during pregnancy (is there a good
            cut point, e.g., 2+
        -   Entry into prenatal care/LEARNED2
        -   Narrative could report whether this differed by race and
            ethnicity, private vs Medicaid insurance, parity. Could also
            look at timing for people who identified
            physical/PREPREG_PHYSCOND and mental health/PREPREG_MHCOND
            conditions in months before index pregnancy
    -   First visit as early as wanted/FIRSTVISIT
        -   Proposed exhibit: breakdown by race and ethnicity and
            private vs Medicaid insurance
        -   Narrative could report whether there were differences by
            pre-preg physical/PREPREG_PHYSCOND and mental
            health/PREPREG_MHCOND health conditions
    -   If not, why couldn’t have visit as early as wanted/NOPRENATAL
        -   Proposed exhibit: simple bar graph in descending order of
            reasons with Overall throughline
    -   Setting for prenatal care/CARESETTING/
        -   Proposed exhibit: simple bar graph in descending order with
            Overall throughline
-   Individual and group prenatal care
    -   Individual versus group care/CARETYPE
        -   Whether had choice/CARETYPE1
            -   Proposed exhibit: by race and ethnicity and type of
                insurance
    -   Preference between individual and group care type (if
        experienced both)/CARETYPEPREF
        -   Proposed exhibit: by race and ethnicity, private vs Medicaid
            insurance (bars, including overall, showing individual,
            group, mix of both)
        -   Narrative could report by parity, education, age
-   Remote and in-person prenatal care/CAREMODE
    -   Reason for televisits/WHYTELE
        -    Proposed exhibit: simple bar graph in descending order with
            Overall throughline
    -   Whether had equipment/supplies for 4 types of home
        monitoring/ATHOMECARE
    -   Confidence about ability to do four types of home
        monitoring/BPCONFID + URINECONFID + WEIGHCONFID + BABYHRCONFID
        -   Proposed exhibit: table with rows combining use of four
            types of home monitoring (percent with equipment/supplies
            among those with remote care?) and confidence of those with
            equipment/supplies
        -   Narrative could report whether greater confidence (fully or
            somewhat, or fully alone?) differed by parity (first time vs
            experienced), age (is there a meaningful cut point?),
            education level (high school or less vs more than high
            school?), and private vs Medicaid insurance
    -   Preference between in-person and televisits (if experienced
        both)/CAREMODEPREF
        -   Proposed exhibit: by race and ethnicity, metro vs non-metro
            residence (bars, including overall, showing in-person,
            televisit, mix) Narrative could report whether preference
            differed by parity, education, whether employed during
            pregnancy, private vs Medicaid insurance
-   Childbirth education
    -   Whether had CBE classes/CURREDUC
        -   Narrative could report whether this differed by parity, by
            private vs Medicaid insurance, by employment during
            pregnancy
        -   If had 1+ prior birth, whether took CBE classes during
            previous pregnancy/PRIOREDUC
            -   Narrative could report whether, limited to multips,
                CURREDUC differed by having taken classes in the past
    -   Sponsor of index pregnancy classes/independence/EDUCTYPE
    -   In-person vs remote/hospital vs community/EDUCMODE
    -   Impact of class/EDUCIMPACT
        -   Proposed exhibit: simple bar graph in descending order with
            Overall throughline
    -   Maybe: comment on cbe trends across LTM surveys (seemed to be
        greatly falling off in past; remote options and maternal health
        crisis publicity might be leading to greater use now)

<!-- -->

-   Pregnancy complications

    -   Whether experienced pregnancy conditions/PREGCONDITION

        -   Proposed exhibit: simple bar graph of percentage reporting
            queried conditions, in descending order with Overall
            throughline

        -   Proposed exhibit: summative score (number of fixed choice
            responses selected) by race and ethnicity, private vs
            Medicaid insurance

            -   Narrative could report whether summative score differed
                by disability status, metro vs non-metro county, vaginal
                or cesarean index birth

-   Mental health during pregnancy

    -   PHQ4 mental health screener/BOTHER (analyzed as PHQ2
        (depression), GAD2 (anxiety), and PHQ4 (psychological distress)
        (see LTM-CA chapter for cut-points and literature)

        -   Proposed exhibit: positive depression screen by race and
            ethnicity, private vs Medicaid insurance

            -   Narrative could report whether positive screen for
                depression differed by disability status, metro vs
                non-metro county, whether IDed depression before preg

    -   Proposed exhibit: positive anxiety screen by race and ethnicity,
        private vs Medicaid insurance

        -   Narrative could report whether positive screen for anxiety
            differed by disability status, metro vs non-metro county,
            whether IDed anxiety before preg

    -   Whether received counseling or therapy during index
        preg/MENTALSUPPORT

    -   Whether took mental health meds during index preg/MENTALSUPPORT
        [Questionnaire repeats previous code: think this one needs to be
        MENTALSUPPORT1]

        -   Proposed exhibit: table showing screening status for
            depression and for anxiety and percentage of people with
            negative and positive screens who got any help

        -   Proposed exhibit: whether got help (counseling/therapy
            and/or meds) by race and ethnicity, private vs Medicaid
            insurance

            -   Narrative could report whether got help
                (counseling/therapy and/or meds) by disability status,
                metro vs non-metro county, whether IDed mental health
                issues before preg

-   Social needs during pregnancy [cross-ref to whether pregnancy needs
    are still an issue at time of survey in postpartum chapter]

    -   Proposed exhibit: simple bar graph with percentage of all
        respondents identifying 9 types of social needs during index
        pregnancy/SOCIALNEED [ordered in most to least order of
        frequency]

    -   Proposed exhibit: average \# of needs identified by race and
        ethnicity, private vs Medicaid payment, income

        -   Narrative could report whether average number of needs
            identified differed by disability status, sexual
            orientation, metro vs non-metro residence, education

-   Employment and pregnancy accommodations

    -   Whether employed during index pregnancy/EMPLOY

    -   If yes, whether FT or PT/EMPLOYHOURS

    -   Whether had paid time off for prenatal visits/EMPLOYBEN

        -   Proposed exhibit: whether had PTO for prenatal visits by
            race and ethnicity, private vs Medicaid payment

            -   Narrative could report whether PTO for prenatal care
                differed by disability status, income, metro vs
                non-metro residence, education

        -   Whether needed temporary accommodations/EMPLOYCHANGE

        -   If needed, whether received pregnancy
            accommodations/EMPLOYCHANGE1

            -   Narrative could report whether access to needed
                accommodations differed by private vs Medicaid payment,
                disability status, metro vs non-metro residence, income,
                education [explore whether “partial” is grouped with
                none or fully or left aside]

-   Late pregnancy

    -   Big baby prediction.Whether told baby might be getting quite
        large/BIGBABY1 [could also fit in a childbirth chapter]

        -   If BIGBABY1=1, whether care provider recommended specific
            response/BIGBABY2
        -   If intervention recommended (BIGBABY2=1,2,or 3), whether it
            occurred/use special programming
        -   If recommended intervention occurred, whether it was before
            39 weeks/use special programming
        -   If BIGBABY1 = 1
            -   Proposed exhibit: show induction and cesarean rates for
                babies that were were and were not predicted to be large
        -   If BIGBABY1 = 1, 
            -   Proposed exhibit: pie chart showing actual birth weight
                for predicted large babies: LBW, normal weight,
                macrosomic
        -   [We don’t have data on provider motivation, but noting that
            providers get the relatively lucrative IP payment from
            scheduling births during time when they’re in hospital]

    -   Planned infant feeding as came to the end of
        pregnancy/PLANNEDFEED (or can put this in BF section of next
        chapter with hospital BF support)

        -   Proposed exhibit: bar graph of intention to exclusively BF
            and partially BF by race and ethnicity, private vs Medicaid
            payment, beginning with an overall bar

            -   Narrative could report intention by whether employed,
                age, education

    -   Pregnancy weight gain PREGWEIGHT - PREPREG_WEIGHT

        -   Proposed exhibit: align with 2009 IOM [recommended ranges by
            prepregnancy
            BMI](https://nap.nationalacademies.org/resource/12584/Report-Brief---Weight-Gain-During-Pregnancy.pdf)
            [let’s find a data viz to show compliance vs deviation from
            these guidelines]

### Chapter 2. Childbirth in hospital settings

-   Basic facts

    -   Mother

        -   Age at birth/AGEBIRTH [Will need to inpute from age given in
            screener for someone with a valid Q1 complete from first
            field period and no Q2 complete in the first round of
            fielding; this added to Q2 in first field period and moved
            to Q1 in second field period]
        -   Parity/NUMB_BIRTH: Report specific numbers (and not binary
            first-time vs experienced)
        -   Average LABORLENGTH for vaginal birth/no induction, vaginal
            birth/induction, in-labor cesarean/no induction, in-labor
            cesarean/induction
        -   LOS/DAYSHOSP: overall, vaginal births, cesarean births,
            range
        -   Mode of birth (report underlying for 2023 and 2024 (with our
            removable exclusions via WONDER) as this is a weighting
            variable?

    -   Baby

        -   Gestational age/calculate with DUEDATE and BIRTHDATE
            -   Proposed exhibit: GA vertical bars by gestational week
                or other viz to show how much we have deviated from a
                bell curve
        -   Birth weight/BIRTHWEIGHT: distribution by VLBW, LBW, normal
            BW, macrosomic
        -   First hour/GOLDENHOUR, location of baby
            -   Proposed exhibit: bar graph with percentage with mom,
                spouse/partner, staff/routine, staff/special percentage
                and with staff for routine care percentage by mode of
                birth; race/ethnicity, beginning with overall
                percentages

            -   Narrative could report private vs Medicaid payment;
                midwife vs physician maternity care provider

            -   If with mom or dad, whether skin-to-skin/SKIN

                -   Proposed exhibit: side-by-side bar graphs with
                    percentage with mom and with spouse/partner, by mode
                    of birth; race/ethnicity, beginning with overall
                    percentages
        -   Location of baby after that/HOSPLOC
        -   NICU admissions (partial or full stay)/NICU
            -   To discuss, whether we feel comfortable trying to ID
                low-risk baby with NICU stay given trend of
                supplier-induced demand and healthier and healthier
                babies getting NICU care (e.g., term, normal birth
                weight and — per eligibility – singleton, )
        -   LOS/BABYHOSP: overall, with no NICU stay, with partial NICU
            stay, with full NICU stay, range

-   Care team – birth attendant, doula support (for many, begins in
    pregnancy, ends pp) and labor support from personal network

    -   Primary type of provider who attended birth/BIRTHATTEND:
        percentages for 1-6

        -   Proposed exhibit: midwife vs physician attendant by race and
            ethnicity, private vs Medicaid payment

            -   Narrative could report midwife vs physician attendant by
                disability status, sexual orientation, metro vs
                non-metro residence, education, income

        -   Moreover, was that person a student/ATTENDSTUDENT=1

    -   Whether had doula support when gave birth/DOULA

        -   Proposed exhibit: whether had birth doula by race and
            ethnicity, private vs Medicaid payment

            -   Narrative could report whether doula support differed by
                no vs any type of disability, income, education, metro
                vs non-metro residence

        -   Possible doula quotes/DOULA3

        -   This may be the place to describe doula use by phase of
            care/DOULA (while describing doula support during pregnancy
            in previous chapter and pp in pp chapter) [trend: from birth
            doulas to extended longitudinal doula support]

    -   Other companions during index birth/OTHERSUPPORT

-   Labor induction

    -   Elective labor induction at term. Provider discussion about
        inducing because it’s around due date/INDUCE

        -   Among those who labored/MODE=1 or LABCSEC=1 (leaving aside
            planned cesareans), percentage whose provider recommended
            elective induction at term/INDUCE5=1

        -   Shared decision making sequence/INDUCE1 and INDUCE2 and
            INDUCE3 and INDUCE4 and INDUCE5 and INDUCE7 based on
            [endorsed performance
            measure](https://mghdecisionsciences.org/wp-content/uploads/2024/02/PQM_2962_User_Guide_SDM_Process_Scale_2023.pdf)
            with 0-4 scoring for INDUCE1 + INDUCE2 + INDUCE3 + INDUCE4

            -   Proposed exhibit: for whom is elective induction at term
                being recommended: INDUCE5=1 by race and ethnicity,
                private vs Medicaid insurance

            -   Narrative could report whether recommendation differs by
                metro vs non-metro residence, by age, education,
                first-time vs experienced 

            -   Proposed exhibit: to what extent are various subgroups
                experiencing SDM, by race and ethnicity, private vs
                Medicaid insurance

            -   Narrative could report whether recommendation differs by
                age, education, first-time vs experienced, any or no
                type of disability

        -   Use INDUCE6 open end for selected quotes in margin about
            trend of elective induction at term

        -   Whether this discussion was followed by attempt to medically
            induce: among INDUCE=1, results for MEDINDUCE and then

            -   Whether among this subset with MEDINDUCE=1, medical
                induction started labor/MEDINDUCE2 and 

            -   Whether the subset of labors induced electively at term
                ended with vaginal or cesarean birth/MODE2023

            -   [Could also be done using MEDINDUCE3=3, but recommend
                incorporating into this sequence focusing on induction
                because it’s term]

    -   Self-induction of labor: whether tried to self-induce index
        pregnancy/SELFINDUCE

        -   If SELFINDUCE=1, whether it started labor/SELFINDUCE1

        -   If SELFINDUCE=1, why tried to self-induce/SELFINDUCE2

            -   Proposed exhibit: simple bar graph of the response
                choices in descending order of frequency with Overall
                throughline

            -   Narrative could report who was more likely to
                self-induce, looking at education, recommendation for
                induction because it was around term, by race and
                ethnicity, by private vs Medicaid payment, by
                predominant physician vs midwife prenatal care provider

    -   Medical induction of labor: whether experienced medical
        induction/MEDINDUCE

        -   If MEDINDUCE=1, method(s) used/MEDINDUCE1

            -   Proposed exhibit: bar graph of  response choices in
                descending order of frequency

        -   If MEDINDUCE=1, whether medical induction started
            labor/MEDINDUCE2

        -   If MEDINDUCE=1, reason for medical induction/MEDINDUCE3

            -   Proposed exhibit: simple bar graph of the response
                choices in descending order of frequency with Overall
                throughline

        -   If MEDINDUCE2=1 (medical induction started labor), duration
            of medical induction/MEDINDUCE4

        -   If MEDINDUCE2=2 (medical induction did not start labor),
            duration of medical induction attempt/MEDINDUCE5 [Note that
            Word version of questionnaire repeats MEDINDUCE4 and this
            should be MEDINDUCE5]

        -   If MEDINDUCE=1, mode of birth (MODE) among people with
            medical induction (whether started labor or not; could limit
            to medical induction for non-health reason and compare mode
            of birth outcome with those experiencing labor and no
            induction)

        -   [Cross-ref to big baby intervention results, briefly noting
            takeaways here]

<!-- -->

-   Hospital childbirth restrictions on movement/positions, oral
    nutrition, choice, optimal care

    -   Among those who labored/MODE=1 or LABCSEC=1, whether had oral
        fluids/LABORPERMIT=1 or oral solids/LABORPERMIT=2 (need to
        creatively distinguish between no/not interested and
        no/interested but not allowed)

    -   Among those who labored/MODE=1 or LABCSEC=1, no
        ambulation/LABORWALK=2 (but did not ask whether was restricted
        to bed)

    -   Among those with a vaginal birth/MODE=1, positions/POSITION used
        by those who did and did not have a choice/POSITIONCHOICE

        -   Proposed exhibit: positions used with and without choice

    -   Consider identifying baby with staff for routine care in first
        hour as restriction or x-ref to that as restriction

    -   Consider no choice in having epis or x-ref to that as
        restriction

    -   Consider hospital staff gave baby formula w/o respondent
        permission/HOSPFEED = 8 (not a part of Baby-Friendly steps;
        LTMAC added this one)

<!-- -->

-   Various childbirth interventions: pain relief, fetal monitoring,
    episiotomy, other labor interventions

    -   Pain relief

        -   Drugfree: among those who labored (either MODE:1 or
            LABCSEC:1), drug-free pain relief methods used/DRUGFREE

            -   Proposed exhibit: simple bar graph showing use of
                non-pharm methods in descending order and those who used
                none

            -   Among those who labored//MODE=1 or LABCSEC=1, percentage
                who did vs did not use drugfree methods

            -   Proposed exhibit: Consider comparing those who did/did
                not use drugfree methods and their attributes (e.g., RE,
                first-time vs experienced mom, physician vs midwife
                birth attendant, no doula vs doula)

            -   Narrative could report how likely respondents were to
                use drugfree methods, by education, race and ethnicity,
                private vs Medicaid payment

        -   Painmeds: among all respondents, which pain medications were
            used/PAINMEDS 

            -   Proposed exhibit: simple bar graph showing use of pharm
                methods in descending order and those who used none with
                Overall throughline

            -   Consider subgroup analyses by vaginal and cesarean
                outcomes and/or between planned cesareans and those who
                labored/MODE = 1 or LABCSEC =1

            -   Among all respondents, percentage who did vs did
                not/PAINMEDS = 7 use pain meds

            -   Proposed exhibit: Consider comparing those who did/did
                not use pain meds and their attributes (e.g., RE,
                first-time vs experienced mom, physician vs midwife
                birth attendant, no doula vs doula)

            -   Narrative could report how likely respondents were to
                use pain meds, by education, race and ethnicity, private
                vs Medicaid payment, parity, mode of birth

    -   Interventions among respondents with cesarean and no
        labor/LABCSEC=2

        -   Whether had IV fluids/CSECTIONINT:1 and bladder
            catheter/CSECTIONINT=2

        -   [Note: respondents unlikely to know the details about many
            additional interventions]

    -   Interventions among respondents who labored/MODE=1 and LABCSEC=1

        -   Whether had AROM post-contractions/LABORINT = 1, IV
            fluids/LABORINT = 2, synthetic OT after labor
            contractions/LABORINT = 3, bladder catheter/LABORINT = 4,
            one+ vaginal exams/LABORINT = 5

            -   Proposed exhibit: simple bar graph of use of these five
                interventions in descending order of frequency with
                Overall throughline

        -   Method used to monitor the fetus (can we say baby at this
            point?)/FETALMON

    -   Interventions among respondents with a vaginal birth, 

        -   Main position used when pushing their baby out/POSITION

            -   Proposed exhibit: simple bar graph of use of various
                positions in descending order of frequency with Overall
                throughline

            -   Other positions used when pushing their baby
                out/POSITION2 (some stage 2 position results proposed
                for Restriction section, above)

        -   Whether they experienced [avoid gift terms like “received”]
            an episiotomy/EPIST=1

            -   Among those with epis, percentage who did not have a
                choice/EPISTCHOICE=2 [no choice could be included above
                under restrictions]

            -   Narrative could report how likely respondents were to
                have had no choice, looking at education, age, race and
                ethnicity, private vs Medicaid payment, parity

        -   Whether a health professional stitched them near the opening
            of their vagina to repair a tear or cut/SUTURE [could remove
            those with epis to estimate the proportion with a tear]

    -   Medicalization and physiologic childbirth

        -   Experience of physiologic childbirth according to
            [reVITALize
            definition](https://www.acog.org/practice-management/health-it-and-clinical-informatics/revitalize-obstetrics-data-definitions)
            (use same programming as in LTM-CA report)

            -   Narrative could report how likely respondents were to
                meet the definition by type of prenatal and type of
                birth maternity care provider, whether had birth doula,
                dilation at admission, private vs Medicaid payment, race
                and ethnicity, education  

        -   At least one measure of experiencing childbirth
            interventions (in the past have enumerated cumulative
            significant interventions (LTM-CA Figure 27), have created
            flow chart (LTM-CA Figure 28 Cascade of Intervention), and
            have enumerated in a table (LTM-CA Table 3) 

        -   Also: spontaneous onset of labor (large-scale uncontrolled
            experiment of shortened gestation) and spontaneous vaginal
            birth rates, 

    -   Labor practices and vaginal or cesarean outcome

        -   We can test the following variables, which are associated
            with vaginal vs cesarean birth, clarifying the analysis is
            not adjusted [could go near end of this chapter as bridge or
            in the following chapter]:

            -   Having a labor doula/DOULA=2 vs no labor doula

            -   Having a midwife birth attendant/BIRTHATTEND=4 vs a
                physician/BIRTHATTEND=1,2,or3

            -   Induced labor [ARRIVE trial says this is protective;
                many others feel that ARRIVE is not generalizable and
                induction poses risk for cesarean]/MEDINDUCE=1

            -   Active versus early labor on first vaginal exam after
                admission/VAGEXAM=6+ vs VAGEXAM=\<6 [could also do
                separate analysis of cesarean rates for each cm as in
                LTM-CA report Figure 19]

            -   Fetal monitoring with hand-held device/FETALMON = 2 vs
                EFM/FETALMON = 1

            -   Being upright and mobile during labor/LABORWALK=1 vs in
                bed

            -   Noting that epidural slows labor and that is why
                synthetic oxytocin is almost universally used as
                co-intervention: could look at epidural without vs with
                synthetic oxytocin among people who labored

<!-- -->

-   Support for breastfeeding among those who planned partial or
    exclusive BF

    -   Breastfeeding intention/PLANNEDFEED = 1

    -   Among those who planned partial or exclusive BF/PLANNEDFEED = 1,
        whether nurses/other staff aligned with Baby-Friendly “steps”
        that women could reasonably know/HOSPFEED = 1-7, 9-10

    -   Separate analysis of HOSPFEED = 8, which was added by LTMAC and
        isn’t precisely aligned with Baby-Friendly steps (report
        HOSPFEED = 8 separately, possibly in restrictions section, as
        restriction on respondent’s feeding choice) 

        -   Proposed exhibit: simple bar graph showing cumulative
            Baby-Friendly steps (leaving HOSPFEED = 8 aside) and
            likelihood of breastfeeding at 1 week, separating exclusive
            and mixed feeding

        -   Narrative could report who was more likely to achieve their
            feeding goals at 1 week, by race and ethnicity, type of
            insurance, type of prenatal care provider, type of birth
            attendant, parity, age, education

-   Respectful care – PCMC-US (maybe ref to appendix on sources of new
    items about selection of items from each scale in longer validated
    tool)

    -   Respect care: developer’s 0-100 [scoring
        guidance](https://drive.google.com/drive/u/0/folders/1Cj9z-7o3ppGYYNRm3JwZH1nzZj1YQbgm?ths=true)

        -   RESPECT (Dignity & Respect scale)

        -   KNOWLEDGE (Dignity & Respect scale)

        -   HEARD (Communication & Autonomy scale)

        -   DECISIONS (Communication & Autonomy scale)

        -   CONSENT (Communication & Autonomy scale)

        -   INFORMED (Communication & Autonomy scale)

        -   TIMELINESS (Responsiveness, Supportive Care scale)

        -   NEGLECT (Dignity & Respect scale)

        -   TRUST (Responsiveness, Supportive Care scale)

        -   FEEDING (Responsiveness, Supportive Care scale)

        -   SAFE (Responsiveness, Supportive Care scale)

        -   DISCRIMINATION (Dignity & Respect scale)

    -   Consider scores for each item, scores for all 12 items

    -   Scores for subscales

        -   Proposed exhibit: by race/ethnicity, private vs Medicaid
            payment

        -   Narrative could report by midwife vs physician birth
            attendant, any vs no type of disability, age, education

    -   Separately analyze/DISCRIMINATION1, which we added [percentage
        choosing each type and cumulative selection?]

    -   Separately analyze per pre-field decision: cultural traditions
        and AIAN analysis/CULTURE (from Dignity & Respect scale) whether
        had customs and then for those that did, whether provider
        respected customs/culture

        -   Proposed exhibit: race and ethnicity [hypothesize greatest
            acknowledgment of cultural traditions and greatest failure
            to accommodate them among AIAN, then Black]

### Chapter 3. Vaginal and cesarean births

-   Mode of birth overview for all survey participants (similar to Table
    4, LTM-CA report)

\
Vaginal XX%

|                            |                        |      |
|----------------------------|------------------------|------|
|                            | Vaginal/no previous CS | VBAC |
| Unassisted                 |                        |      |
| Vacuum or Forceps Assisted |                        |      |

Total Cesarean XX%

|           |                      |                     |
|-----------|----------------------|---------------------|
|           | Primary Cesarean XX% | Repeat Cesarean XX% |
| Unplanned |                      |                     |
| Planned   |                      |                     |

-   Total cesarean and vaginal birth rates

    -   Proposed exhibit: mode of birth by race and ethnicity, private
        vs Medicaid payment

    -   Narrative could report midwife vs physician childbirth provider

-   Vaginal birth

    -   Whether assisted with forceps or vacuum/VAGASSIST

    -   Very low VBAC rate [and reference to discussion of access,
        choice, results in following section]

    -   Could reference section in previous chapter with labor practices
        that were and were not associated with greater likelihood of
        vaginal birth

-   Cesarean variations 

    -   Mind the denominator. Consider replicating LTM-CA Table 5 Mind
        the denominator for 4 different cesarean rates: total, primary,
        repeat, NTSV [illustrates: not to confuse total and NTSV,
        sky-high repeat rate, NTSV just deals with a small proportion]

    -   Unplanned in-labor cesareans/CSECTIONTYPE=2

        -   Reported reason for the cesarean/UNPLANNEDREASON

            -   Proposed exhibit: simple bar graph in descending order
                of response choices with Overall throughline

            -   [Possibly something here about length of labor with
                unplanned cesareans/LABORLENGTH among those who labored
                before planned/CSECTIONTYPE=2 and LABCSEC=1]

            -   [Maybe cross-ref to planned cesarean labor
                interventions, in prev chapter]

    -   Planned cesareans and birth options after
        cesarean/CSECTIONTYPE=1

        -   Reported reasons for having a planned cesarean/PLANNEDC

            -   Proposed exhibit: simple bar graph in descending order
                of response choices with Overall throughline

        -   Possible repeat cesarean quotes for margins/REPEATCSEC

        -   VBAC rate

            -   Proposed exhibit: VBAC rates by race and ethnicity,
                private vs Medicaid payment with overall throughline

                -   Narrative could report by midwife vs physician
                    prenatal provider and midwife vs physician
                    childbirth provider

            -   Proposed exhibit: who reported main reason for repeat
                was previous by race and ethnicity, private vs Medicaid
                payment

                -   Narrative could report who was more likely to have
                    repeat due to prior cesarean by midwife vs physician
                    prenatal provider and midwife vs physician
                    childbirth provider

        -   Whether those with repeat cesarean (LTM-CA report has some
            food for thought on display of VBAC results)

            -   Had option of VBAC/VBACCHOICE

            -   Reason VBAC not available (VBACCHOICE=2 and
                VBACINTEREST=1

                -   See complex graphic for these items in LTM-CA report
                    (Figure 33)

                -   Important to look at

            -   Was interested in option VBAC/VBACINTEREST

                -   If had repeat and was interested in VBAC, whether
                    tried to plan a VBAC/VBACEFFORT

                -   Whether took any steps to plan for VBAC/VBACEFFORT
                    (among MODE=2for any previous birth, MODE2023=2, and
                    VBACINTEREST=1)

                -   If didn’t have option, was interested in VBAC and
                    had a repeat, why didn’t have option/VBACACCESS

### Chapter 4. Early Postpartum Period (after leaving hospital)

-   Postpartum doula support

    -   Whether had doula support after birth when home with
        baby/DOULA=3

-   Proposed exhibit: whether had postpartum doula support by race and
    ethnicity, private vs Medicaid payment with overall throughline

    -   Narrative could report by any vs no type of disability, income,
        education, metro vs non-metro residence, 

    -   If yes, how doula supported/DOULA2

    -   Possible doula quotes for margins/DOULA3

    -   [appropriate to concisely report consolidated doula results
        across phases of care; propose that this occurs when reporting
        birth doula experiences; maybe x-ref here]

\

-   Postpartum office visits

    -   Number of visits/PPVISIT

-   Proposed exhibit: bar graph showing 0, 1, 2, 3, 4+ by
    race/ethnicity, private vs Medicaid payment,  with Overall bar (CA
    Figure 47 aligns bars vertically between 0 to left and 1+ to right)

    -   Narrative could report whether there were differences by midwife
        vs physician prenatal provider

-   Can comment on the flaws of using billing codes to describe extent
    of pp visits, because they greatly underestimate actual visits; more
    accurate and more extensive to ask mothers

    -   Timing of first visit among 2+ visits/PPVISITTIME and timing of
        single visit/PPVISITTIME (can reference ACOG recommendation for
        pp visits and how much our respondents’ experiences align)

    -   Content of pp visits/VISITTOPIC, ordered from least to most
        likely to have been addressed (need creative way of
        distinguishing no and needed from no and didn’t need across the
        seven topics)

-   Narrative could report whether there are differences between No and
    needed vs no and didn’t need, by first-time vs experienced moms,
    education

-   Narrative could report whether there are differences between yes,
    covered and either no, not covered, by midwife vs physician most
    often prenatal provider

\

-   Infant feeding

    -   Feeding intention and feeding at one week, Relationship between
        feeding intention/PLANNEDFEED and feeding at one week
        postpartum/FEED1WEEK: concordant, discordant and in what
        direction

-   Proposed exhibit: to look at missed opportunities, compare
    concordant BF (either planned exclusive and exclusive at one week or
    planned mixed and mixed at one week) to who dropped off of BF
    intention: planned exclusive and mixed or formula at one week and
    planned mixed and formula only at one week, by race/ethnicity;
    private vs Medicaid payment

    -   Narrative could report whether there were differences by midwife
        vs physician birth attendant, first-time vs experienced moms; 
        fidelity to Baby-Friendly steps/HOSPFEED (apart from 8, added by
        LTMAC)

-   Proposed exhibit: to look at value-added situations, compare
    concordant planned formula and formula at one week or planned mixed
    and mixed at one week to who improved over BF intention: planned
    formula and any BF or planned mixed and exclusive BF at one week, by
    midwife vs physician birth attendant, and fidelity to Baby-Friendly
    steps/HOSPFEED (apart from 8, added by LTMAC)

    -   Narrative could report whether there were differences by
        first-time vs experienced moms

-   Proposed exhibit: HOSPFEED showing possible relationship between
    cumulative \# of yeses (apart from response 8, which was a LTMAC
    addition to Baby-Friendly criteria) and achievement of breast milk
    feeding goals at one week

-   Separate result for HOSPFEED = 8 (if enough reported yes, Proposed
    exhibit: by race and ethnicity and private vs Medicaid payment) OR
    could just report under Hospital Childbirth Restrictions in
    Childbirth in Hospital Settings chapter 

    -   Achieving goals for breast milk feeding/CURRENTFEED: exclusive,
        any, no breast milk (with some indication of baby age for each

-   Duration of exclusive breast milk feeding/EXCLUSIVEBF

-   Whether fed breast milk alone as long as wanted/EXCLBFGOAL

    -   Proposed exhibit: simple bar graph describing how likely
        respondents were to exclusively breastfeed as long as they
        wanted, by race and ethnicity, first-time vs experienced moms,
        with Overall throughline

    -   Narrative could report whether there were differences by age,
        education, income

-   Baby’s age at full weaning

-   Whether fed any breast milk as long as wanted/BFGOAL

    -   Proposed exhibit: simple bar graph describing how likely
        respondents were to feed any breast milk as long as they wanted,
        by race and ethnicity, first-time vs experienced moms, with
        Overall throughline

    -   Narrative could report whether there were differences by age,
        education, income

\

-   Mental health at time of survey

    -   Positive screens for depression, anxiety, psychological distress

-   PHQ4 mental health screener/PPBOTHER analyzed as PHQ2 (depression)

    -   Proposed exhibit: simple bar graph describing who screened
        positive for depression by race and ethnicity and private vs
        Medicaid payer with Overall throughline

-   PHQ4 mental health screener/PPBOTHER analyzed as GAD2 (anxiety)

    -   Proposed exhibit: simple bar graph describing who screened
        positive for anxiety by race and ethnicity and private vs
        Medicaid payer with Overall throughline

-   PHQ4 mental health screener/PPBOTHER analyzed as PHQ4 (psychological
    distress) (see LTM-CA chapter for cut-points and literature)

    -   Proposed exhibit: simple bar graph describing who screened
        positive for psychological distress by race and ethnicity and
        private vs Medicaid payer with Overall throughline

    -   Receiving mental health help

-   Whether received counseling or therapy during index preg/PPTHERAOT

-   Whether took mental health meds during index preg/PPMEDS

    -   Proposed exhibit: received help (counseling and/or therapy) by
        positive and negative screens for psychological distress, by
        race and ethnicity and private vs Medicaid payer

    -   Narrative could report whether there were differences, by age,
        education, income

    -   Persistence of mental health conditions

-   Relationship between prepreg mental health/PREPREG_MHCOND and mental
    health at time of survey/PPBOTHER for PHQ4/psychological distress

-   Relationship between preg mental health and mental health at time of
    survey/BOTHER and mental health at time of survey/PPBOTHER in two
    ways 

    -   BOTHER = PHQ2 and PPBOTHER = PHQ2 for depression

    -   BOTHER = GAD2 and PPBOTHER = GAD2 for anxiety\

-   Continuing social needs Still an issue at time of survey (comment:
    possible that some needs newly arose after birth and we did not
    repeat entire screener)

    -   Compare percentage resolved and percentage unresolved for social
        needs identified during pregnancy and whether still experiencing
        the need at time of survey/SNMEAL; SNLIVE; SNUTILITIES;
        SNTRANSPORT; SNCHILDCARE; SNINCOME; SNDRUGS; SNUNSAFE; SNABUSE

-   Proposed exhibit: whether respondents had continuing specific social
    needs identified during pregnancy at time of survey, by race and
    ethnicity and private vs Medicaid payer

-   Proposed exhibit: who had continuing social needs at time of survey
    by counts (e.g., 0, 1, 2, 3+), by race and ethnicity and private vs
    Medicaid payer

    -   Narrative could report whether there were differences by income,
        age, education, first-time vs experienced moms

-   Weight loss at time of survey/PREGWEIGHT - CURRWEIGHT by time
    elapsed since birth in two-month increments (previously we found
    incremental loss/mo over finite period, ending with no further loss
    and a net gain of about 6? lbs/pregnancy)
